% Resumo em ingles

\begin{otherlanguage*}{english}
  This is a project of an e-commerce web system, built for a real food company based in the city of Itajubá in Minas Gerais. The goal is to create a fast and secure website, which gives to the user a unique experience and provides in a clear and informative way the product of the company. Some content will be created to enrich the site and draw the customer's attention to the product.

  Use the Drupal framework and content manager built in PHP language, chosen for its robustness and large developer community. Its latest version, Drupal 8, is a flexible and innovative platform with robust caching systems and multiple APIs that provides secure methods for a website builder.

  Our goals can be achieved with the help of modules from the Drupal community and the latest technologies and techniques of web systems that fits the project. The development flow will be the safest for code robustness, using Vagrant software to ensure constant environments and git for version control. The task automator Gulp and package managers NPM and Composer will be some of the tools we'll use to ease the installation and programming processes.

  We expect site performance to be above average and tests will be constantly done to ensure this. The most widely used will be GTMetrix, the most complete performance testing tool currently available, which still gives some tips to improve it.
  
  \vspace{\onelineskip}

  \noindent
  \textbf{Keywords}: e-commerce. drupal. web. php. performance. seo. twig. less.
\end{otherlanguage*}
